The Supervisionary proof-checking kernel

### 2021-10-25 paper/prisc-2022.tex
prisc-2020: minor rewording according to slack discussion

Switching tack, operating systems are also typically designed around a trusted \emph{kernel}, a privileged component responsible for---amongst other things---mediating interaction betwixt user-space software and hardware.
Untrusted processes interact with the system by issuing kernel \emph{system calls} across a hardware privilege boundary.
In this way, the operating system kernel \emph{supervises} user-space processes.
Usually, the source executables of untrusted processes need not have been written in the same language as the kernel.

@@

Existing tools in the HOL familiy could be refactored around Supervisionary by changing their kernels to act as a shim between untrusted automation and the Supervisionary kernel.
Arguably, this increases the robustness of existing tools, enforcing separation by isolation, rather than module boundaries.
More interestingly, this also means that Supervisionary acts as a mechanism for ``transporting'' definitions and theorems between systems within the wider HOL family: systems are capable of referring to, and manipulating, kernel objects produced by other systems through Supervisionary kernel handles.
With this, we can also bootstrap a full theorem-proving environment, with associated libraries of content, on top of Supervisionary without writing it from scratch.

>>>>

Changing tack, operating systems are also typically designed around a trusted \emph{kernel}, a privileged component responsible for---amongst other things---mediating interaction betwixt user-space software and hardware.
Untrusted processes interact with the system by issuing kernel \emph{system calls} across a hardware privilege boundary.
In this way, the operating system kernel \emph{supervises} user-space processes.

@@

Existing tools in the HOL family could be refactored around Supervisionary by changing their kernels to act as frontends to the Supervisionary kernel for untrusted automation routines.
Arguably, this increases the robustness of existing tools, enforcing separation by isolation, rather than module boundaries.
More interestingly, this also means that Supervisionary acts as a mechanism for ``transporting'' definitions and theorems between systems within the wider HOL family: systems are capable of referring to, and manipulating, kernel objects produced by other systems through Supervisionary kernel handles.
With this, we can also bootstrap a full theorem-proving environment, with associated libraries of content, on top of Supervisionary without writing it from scratch.
